---
title: "Logitech Product Reviews"
author: Meenakshi Rajgopal
date: "`r format(Sys.time(), '%d. %B %Y')`"
output: 
    html_document:
      number_sections: yes
      toc: yes
      toc_float: yes
      fig_caption: true
      theme: flatly
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
knitr::opts_chunk$set(fig.pos = 'H')
# import all libraries
library(ggplot2)
library(reshape2)
library(zoo) # date transformations
library(sentimentr)
```

# Joining data structures
Q1. How would you join the two data structures (sales data and review data)  to setup the analysis ?

```{r readdatas, echo=TRUE}
# read all datas here
prdid <- read.csv("data/PLSKU.csv", sep = ";", header = T)[, 1:2]
prdreviews <- read.csv("data/PRODREVS.csv", header = T, stringsAsFactors = F)
sales <- read.csv("data/SKUSALES.csv", sep = ";", skip = 1)


# convert sales to numeric and replace ',' with '.'
sales_only <- as.data.frame(sapply(sales[c(2:38)], function(x) as.numeric(gsub(",", "", x))))
sales <- cbind(sales$PROD_SKU, sales_only)
colnames(sales)[1] <- 'PROD_SKU'

```


## Product growth over the years
Merge sales with productid. Then Aggregate sales for each product line. 

Plot sales trend over the years for each product.

```{r plot sales, echo=TRUE, fig.width=8, fig.height=5}
# merge by column Unique ID
saleswithid <- merge(prdid, sales, by="PROD_SKU")
colnames(saleswithid)[2] <- "product_line"

sales_agg <- aggregate(. ~ product_line, data = saleswithid[c(2:39)], sum) 

# melt aggregated sales and plot
sales_melt <- melt(sales_agg, id.vars = 'product_line')
sales_melt$variable <- as.yearmon(sales_melt$variable, "%B.%Y")
sales_melt$value <- as.numeric(sales_melt$value)
sales_melt$product_line <- as.factor(sales_melt$product_line)


ggplot(sales_melt, aes(x = variable, y = value))+
  geom_line(aes(color = product_line), size=1)+
  theme_minimal()

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Sales per quarter

```{r plotquaterrls, echo=TRUE, fig.width=8, fig.height=5}
sales_melt$qtr <- as.yearqtr(sales_melt$variable)
qtr_sales <-  aggregate(value ~ product_line + qtr, data = sales_melt, sum)

# plot quaterly sales
ggplot(qtr_sales, aes(x = qtr, y = value))+
  geom_line(aes(color = product_line), size=1)+
  scale_y_continuous(labels = scales::comma) + 
  theme_minimal()

```

# Product Sentiments

```{r text_sentiments, echo=TRUE, fig.width=8, fig.height=5}
sent <- get_sentences(prdreviews$review_text)
reviewsentiments <- sentiment_by(sent)

sent_df <- data.frame(product_line = prdreviews$product_line, date = prdreviews$review_date,
                      ave_sentiment = reviewsentiments$ave_sentiment)
sent_df$date <- format(as.Date(sent_df$date),'%B.%Y')
sent_df$date <- as.yearmon(sent_df$date, "%B.%Y")

# add prduct line variable for ggplot
# sent_df$variable <- NA 
# sent_df[sent_df$product_line == 'Protoss', ]$variable <- 1
# sent_df[sent_df$product_line == 'Heat', ]$variable <- 2
# sent_df[sent_df$product_line == 'Hyjal', ]$variable <- 3
# 

ggplot(sent_df, aes(x = date, y = ave_sentiment)) +
  geom_point(aes(color = product_line))+ 
  facet_wrap(~product_line) +
  theme_minimal()

```


```{r plotsentiments, echo=TRUE, fig.width=8, fig.height=5}
ggplot(sent_df, aes(y=ave_sentiment)) + geom_boxplot() + facet_wrap(~product_line) + theme_minimal()

```


## Aggregated product sentiments
```{r}
# Aggregate sentiment scores for each month and plot trend


```


